\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{tikz}
\usetikzlibrary{positioning, shapes.geometric, arrows.meta, chains, fit, calc, decorations.pathreplacing}

% =======================================================================
% Margins
\NeedsTeXFormat{LaTeX2e}
\oddsidemargin -10 pt
\evensidemargin 10 pt
\marginparwidth 1 in
\oddsidemargin -1.5 true cm
\evensidemargin -1.5 true cm
\marginparwidth 0.75 in
\textwidth 7.5 true in
\textheight 26.0 true cm
\topmargin -2.5 true cm

% =======================================================================
% Code listings style
\lstset{
  language=Java,
  basicstyle=\ttfamily\small,
  keywordstyle=\color{blue}\bfseries,
  commentstyle=\color{gray},
  stringstyle=\color{red!70!black},
  breaklines=true,
  frame=single,
  backgroundcolor=\color{gray!5},
  numbers=left,
  numberstyle=\tiny\color{gray},
  tabsize=4,
  showstringspaces=false
}

\title{Programming Paradigms (Neapolis University Pafos) \\
  Assignment 3: Audio Processing System}

\date{April 2026}

\begin{document}
\maketitle

% ========================================================================
% Architecture Diagram
% ========================================================================
\begin{center}
\begin{tikzpicture}[
    node distance = 6mm and 12mm,
    box/.style = {rectangle, draw, align=center, minimum width=2.2cm, minimum height=1cm, rounded corners=2pt},
    source/.style = {box, fill=red!20},
    proc/.style = {box, fill=green!20},
    sink/.style = {box, fill=blue!20},
    chan/.style = {rectangle, draw, fill=yellow!15, minimum width=1.2cm, minimum height=0.7cm,
                   align=center, font=\scriptsize, rounded corners=1pt},
    vis/.style = {box, fill=orange!20, dashed},
    arr/.style = {-Stealth, thick},
]
    % Sources
    \node[source] (src1) {WAV File\\Source};
    \node[source, below=8mm of src1] (src2) {Microphone\\Source};
    \node[source, below=8mm of src2] (src3) {Sine Wave\\Generator};

    % Input channel
    \node[chan, right=12mm of src2] (ch1) {Channel};

    % Processor chain
    \node[proc, right=8mm of ch1] (p2) {Volume\\Control};
    \node[proc, above=8mm of p2] (p1) {Noise\\Gate};
    \node[proc, below=8mm of p2] (p3) {Mono $\to$\\Stereo};
    \node[chan, right=8mm of p2] (ch4) {Channel};

    % Sinks
    \node[sink, right=12mm of ch4, yshift=8mm] (snk1) {Speaker\\Sink};
    \node[sink, right=12mm of ch4, yshift=-8mm] (snk2) {File\\Sink};

    % Visualization (tapping into channel)
    \node[vis, below=12mm of ch4, xshift=4mm] (vis) {Waveform\\Display};

    % Arrows: sources to input channel
    \draw[arr] (src1.east) -- (ch1.north west);
    \draw[arr] (src2.east) -- (ch1.west);
    \draw[arr] (src3.east) -- (ch1.south west);

    % Pipeline flow
    \draw[arr] (ch1.north east) -- (p1);
    \draw[arr] (ch1.east) -- (p2);
    \draw[arr] (ch1.south east) -- (p3);
    \draw[arr] (p1) -- (ch4);
    \draw[arr] (p2) -- (ch4);
    \draw[arr] (p3) -- (ch4);

    % Sinks
    \draw[arr] (ch4.north east) -- (snk1.west);
    \draw[arr] (ch4.south east) -- (snk2.west);

    % Visualization tap
    \draw[arr, dashed, orange!70!black] (ch4.south) -- (vis.north);

    % Pipeline brace
    \draw[decorate, decoration={brace, amplitude=6pt, mirror}, thick, gray]
      ([yshift=-7mm]p3.south west) -- ([yshift=-4mm]vis.south east)
      node[midway, below=8pt, font=\small\itshape, gray] {ProcessorChain (composable pipeline)};

\end{tikzpicture}
\end{center}

\section{Introduction}

In this assignment you will design and implement a \textbf{versatile audio processing system} in Java
that demonstrates core OOP principles in a realistic, non-trivial domain.

The system processes audio as a stream of \textbf{Pulse-Code Modulation (PCM) samples} flowing through a configurable pipeline:
\textit{sources} produce audio data, \textit{processors} transform it,
and \textit{sinks} consume the result. All components communicate via thread-safe
\textit{channels}, and the pipeline is assembled using the \textit{Builder} pattern.

Your system must handle audio at the \textbf{sample level}~--- understanding
that a ``byte array'' is really a sequence of 16-bit signed integers in little-endian byte order.

Use the provided \href{https://github.com/CSAI-programming-paradigms/oop_project}{Java-project template}
as your starting point. It contains interfaces, core infrastructure, and one working example
(VolumeControlStrategy with proper PCM handling) to get you started.


\section{Background: PCM Audio Fundamentals}

Before writing audio processors, you must understand how digital audio is represented in memory.

\subsection{What is PCM?}

\textbf{Pulse Code Modulation (PCM)} is the standard way to represent audio digitally.
An analog sound wave is sampled at regular intervals and each sample is quantized to a fixed number of bits.

\begin{center}
\begin{tikzpicture}[scale=0.8]
    % Axes
    \draw[-Stealth] (0,-2.2) -- (0,2.5) node[left] {\small Amplitude};
    \draw[-Stealth] (-0.3,0) -- (10.5,0) node[below right] {\small Time};

    % Sine wave
    \draw[blue!60, thick, domain=0:10, samples=200] plot (\x, {1.8*sin(1.2*\x r)});

    % Sample points
    \foreach \x in {0,0.5,...,10} {
        \pgfmathsetmacro{\y}{1.8*sin(1.2*\x r)}
        \fill[red!70!black] (\x, \y) circle (2pt);
        \draw[red!70!black, thin] (\x, 0) -- (\x, \y);
    }

    \node[below, font=\small] at (5,-2.5) {
        Each red dot is one \textbf{sample} (e.g., a 16-bit signed integer)
    };
\end{tikzpicture}
\end{center}

\subsection{Key Parameters}

\begin{itemize}
    \item \textbf{Sample Rate}: Number of samples per second (e.g., 44\,100~Hz for CD quality).
    \item \textbf{Bit Depth}: Bits per sample. \textbf{16-bit signed} is standard.
          Values range from $-32\,768$ to $+32\,767$.
    \item \textbf{Channels}: Mono (1 channel) or Stereo (2 channels, interleaved: L, R, L, R, \ldots).
    \item \textbf{Byte Order}: 16-bit samples are stored as 2 bytes in \textbf{little-endian} order
          (low byte first).
\end{itemize}

\subsection{Reading a 16-bit Sample from a Byte Array}

\begin{lstlisting}
// bytes[i] is the low byte, bytes[i+1] is the high byte
int sample = (bytes[i] & 0xFF) | (bytes[i + 1] << 8);

// Writing back after processing:
bytes[i]     = (byte) (sample & 0xFF);
bytes[i + 1] = (byte) ((sample >> 8) & 0xFF);
\end{lstlisting}

This is the fundamental operation you will use in every audio processor.
\textbf{Ignoring byte order or treating individual bytes as samples is a common mistake}
that produces noise instead of processed audio.


\section{OOP Principles and Design Patterns}

This project exercises multiple OOP concepts and design patterns:

\begin{enumerate}
    \item \textbf{Encapsulation}: Audio format details, buffer management, and thread synchronization
          are hidden inside Channel and AudioStream implementations.
    \item \textbf{Inheritance \& Interfaces}: \texttt{AudioStream}, \texttt{AudioProcessingStrategy},
          and \texttt{DataPin} define contracts; concrete classes provide implementations.
    \item \textbf{Polymorphism}: Different sources, processors, and sinks are interchangeable
          through their interfaces.
    \item \textbf{Strategy Pattern}: Audio processors implement \texttt{AudioProcessingStrategy},
          allowing algorithms to be swapped at runtime.
    \item \textbf{Observer Pattern}: \texttt{ObservableChannel} notifies \texttt{DataPin} subscribers
          when data arrives, enabling reactive data flow.
    \item \textbf{Composite Pattern}: \texttt{ProcessorChain} composes multiple strategies into one,
          applying them sequentially.
    \item \textbf{Builder Pattern}: \texttt{AudioPipeline.Builder} provides a fluent API for
          assembling pipelines declaratively.
    \item \textbf{Factory Pattern}: Create sources, sinks, and processors through factory methods
          for cleaner instantiation.
\end{enumerate}


\section{Core Components}

\subsection{Audio Stream Interface}

\begin{lstlisting}
public interface AudioStream {
    byte[] read() throws IOException;
    void write(byte[] data) throws IOException;
    void close() throws IOException;
}
\end{lstlisting}

Foundation for any class that handles audio I/O. Implementing classes provide
the specifics: \\
\texttt{FileAudioStream} for files, \texttt{MicrophoneAudioStream}
for microphone input, \texttt{NetworkAudioStream} for network streaming, etc.

\subsection{Channel System}

\textbf{Channel} buffers audio data between components using a \texttt{BlockingQueue},
enabling asynchronous, thread-safe producer-consumer flow.
Subchannels carry metadata (e.g., timestamps, checksums, audio format info).

\textbf{ObservableChannel} extends Channel with the Observer pattern:
when data arrives, all subscribed \texttt{DataPin} instances are notified.

\subsection{Audio Processing Framework}

The \textbf{Strategy Pattern} powers the processing framework:

\begin{lstlisting}
public interface AudioProcessingStrategy {
    byte[] processAudio(byte[] inputData);
}
\end{lstlisting}

Each concrete strategy implements a specific audio transformation.
The provided \texttt{VolumeControlStrategy} demonstrates proper 16-bit PCM sample handling
with overflow clipping~--- use it as a reference for your own processors.

\textbf{ProcessorChain} implements the \textbf{Composite Pattern}, chaining multiple strategies:

\begin{lstlisting}
ProcessorChain chain = new ProcessorChain()
    .add(new NoiseGateStrategy(500))
    .add(new VolumeControlStrategy(1.5))
    .add(new MonoToStereoStrategy());

byte[] result = chain.processAudio(inputData);
\end{lstlisting}

\subsection{Pipeline Composition (Builder Pattern)}

The \texttt{AudioPipeline} class provides a fluent \textbf{Builder API}
for assembling complete audio pipelines:

\begin{lstlisting}
Pipeline pipeline = AudioPipeline.builder()
    .source(new WAVFileReader(file, inputChannel))
    .channel(inputChannel)
    .processor(processorChain)
    .channel(outputChannel)
    .sink(new SpeakerConsumer(outputChannel))
    .sink(new FileWriterConsumer(outFile, outputChannel))
    .build();

pipeline.start();
// ... audio flows through the pipeline ...
pipeline.stop();
\end{lstlisting}

Students must complete the \texttt{AudioPipeline} implementation, handling thread management,
graceful shutdown, and error propagation.

\subsection{Pins and Observer Pattern}

\texttt{DataPin} is the observer interface; \texttt{AudioProcessorPin} is a concrete observer
that retrieves data from an \texttt{ObservableChannel}, applies a processing strategy,
and forwards the result. This enables reactive, event-driven data flow through the pipeline.

\subsection{Sine Wave Generator}

The blueprint includes a \texttt{SineWaveGenerator}~--- an audio source that produces
a mathematically perfect sine wave at a configurable frequency.
Use it to \textbf{test your processors without needing actual WAV files}:

\begin{lstlisting}
// Generate 2 seconds of 440 Hz tone (A4 note)
SineWaveGenerator gen = new SineWaveGenerator(440.0, 2.0);
byte[] audioData = gen.generate();
\end{lstlisting}

\subsection{Utility Components}

\begin{itemize}
    \item \textbf{WAVUtils}: Read and write WAV file headers (44-byte RIFF format).
          Provided in the blueprint~--- essential for any file I/O.
    \item \textbf{SystemLogger}: Centralized logging utility.
    \item \textbf{Converter$\langle$T, R$\rangle$}: Generic conversion interface for transformations
          like Speech-to-Text.
\end{itemize}


\section{The Problems}

\textit{Note: we reserve the right to deduct points for incomprehensible code,
careless project structure, or solutions that clearly do not understand
the underlying audio representation (e.g., treating individual bytes as samples).}

% -----------------------------------------------------------------------
\subsection{Problem 1: Core Audio Pipeline \hfill \textbf{(20 points)}}

Implement a working end-to-end audio pipeline.

\begin{enumerate}
    \item Implement at least \textbf{2 audio sources}. Choose from:
    \begin{itemize}
        \item WAV file reader (reading from \texttt{.wav} files on disk)
        \item Microphone capture (real-time input from system microphone)
        \item Network stream (receiving audio over TCP/UDP)
        \item Sine wave / tone generator (already provided as reference)
    \end{itemize}

    \item Implement at least \textbf{2 audio consumers}. Choose from:
    \begin{itemize}
        \item WAV file writer (writing processed audio to \texttt{.wav} files)
        \item Speaker output (real-time playback through system speakers)
        \item Network sender (streaming audio over the network)
    \end{itemize}

    \item Create a \textbf{complete working example} that reads audio from a source,
          processes it through at least one processor, and sends the result to a consumer.

    \item All sources and consumers must use the Channel infrastructure for data flow
          and handle \textbf{audio format metadata} properly (sample rate, bit depth, channels).
\end{enumerate}

% -----------------------------------------------------------------------
\subsection{Problem 2: Audio Processors and Pipeline Composition \hfill \textbf{(25 points)}}

Implement audio processing strategies and composable pipelines.

\begin{enumerate}
    \item Implement a few from \textbf{4 audio processing strategies},
          all working with proper 16-bit signed PCM samples:
    \begin{itemize}
        \item \textbf{Volume Control}~--- scale sample amplitude with overflow clipping
              (provided as reference in the blueprint)
        \item \textbf{Noise Gate}~--- zero out samples below an amplitude threshold
        \item \textbf{Mono $\leftrightarrow$ Stereo Conversion}~--- duplicate mono samples to both channels,
              or average stereo channels to mono
        \item \textbf{One non-trivial DSP algorithm}~--- choose one:
        \begin{itemize}
            \item \textit{Echo / Delay}: mix signal with a delayed copy of itself
            \item \textit{Reverb}: simulate room acoustics (e.g., Schroeder or Freeverb algorithm)
            \item \textit{Speed / Pitch modification}: resample audio with interpolation
            \item \textit{Simple Equalizer}: boost/cut frequency bands using filters
            \item \textit{Compressor / Limiter}: reduce dynamic range
            \item \textit{Fade In / Fade Out}: gradually change volume over time
            \item Or propose your own variant!
        \end{itemize}
    \end{itemize}

    \item Complete the \texttt{ProcessorChain} implementation to chain multiple strategies
          via the Composite Pattern. Verify that the order of processors matters
          (e.g., noise gate before volume boost gives different results than the reverse).

    \item Complete the \texttt{AudioPipeline.Builder} to declaratively construct pipelines
          with sources, processor chains, and multiple sinks.
\end{enumerate}

% -----------------------------------------------------------------------
\subsection{Problem 3: Testing \hfill \textbf{(25 points)}}

Write comprehensive tests for each component.

\begin{enumerate}
    \item \textbf{Unit tests} for:
    \begin{itemize}
        \item Each audio processing strategy (verify correct sample transformation,
              clipping behavior, edge cases with silence / maximum amplitude)
        \item Channel and ObservableChannel (buffering, blocking, subchannel operations,
              observer notifications)
        \item ProcessorChain (verify order of application, empty chain, single processor)
        \item Sources and consumers (mock hardware where necessary)
    \end{itemize}

    \item \textbf{Integration tests} for:
    \begin{itemize}
        \item Complete pipeline: source $\to$ processor chain $\to$ consumer
        \item Use \texttt{SineWaveGenerator} as a deterministic source for reproducible tests
        \item Verify that audio data passes through the pipeline correctly
    \end{itemize}

    \item Use \textbf{JUnit 5} and \textbf{Mockito} (both included in the blueprint POM).
          The blueprint includes sample tests~--- follow their patterns.
\end{enumerate}

% -----------------------------------------------------------------------
\subsection{Problem 4: UI with Real-time Visualization \hfill \textbf{(30 points)}}

Build a graphical interface for configuring and monitoring the audio pipeline.

\begin{enumerate}
    \item \textbf{Pipeline Configuration UI} (15 points):
    \begin{itemize}
        \item Select audio source type and configure its parameters
              (e.g., file path, microphone device, network address)
        \item Select and configure processors with adjustable parameters
              (e.g., volume slider, noise threshold, echo delay time)
        \item Select audio consumer(s) and configure output
        \item Start / Stop controls for pipeline execution
        \item Status display and logging panel
    \end{itemize}

    \item \textbf{Real-time Audio Visualization} (15 points):
    \begin{itemize}
        \item Display a \textbf{waveform view} (amplitude vs.\ time) that updates
              in real-time as audio flows through the pipeline
        \item \textit{OR} display a \textbf{spectrum / level meter} (frequency or amplitude bars)
        \item The visualization must tap into the channel data without disrupting
              the audio flow (read from a subchannel or use the Observer pattern)
        \item Update smoothly at a reasonable frame rate ($\geq$10 FPS)
    \end{itemize}

    \item Use \textbf{JavaFX} (included in the blueprint) or another Java UI library of your choice
          (Swing, LibGDX, etc.). If you choose an alternative, justify it briefly in your README.
\end{enumerate}

\textit{Tip: JavaFX Canvas or a custom Node works well for waveform drawing.
Use \texttt{Platform.runLater()} for thread-safe UI updates from audio processing threads.}


% -----------------------------------------------------------------------
\subsection{Bonus Challenge \hfill \textbf{(not graded)}}

The most educational challenge is not something we can auto-grade or peer assess,
so we encourage doing it even though it will not count toward your grade:

\begin{itemize}
    \item Reimplement (part of) your solution in a different OOP language:
          Kotlin, Scala, Rust, C\#, or Python.
    \item Implement pipeline serialization: save and load pipeline configurations
          to/from JSON or XML files.
    \item Add a visual pipeline editor where users drag-and-drop
          source/processor/sink nodes and connect them with wires
          (one of the best student solutions from last year did this!).
    \item Integrate a real speech recognition library (e.g., Vosk) as a consumer.
\end{itemize}


\section{Choosing a Framework}

This project uses the \textbf{Spring Framework} for dependency injection and configuration management.
Spring Boot provides auto-configuration, bean management, and externalized properties.

\subsection{Alternatives}
If you prefer a different framework, you may use one of these alternatives
(document your choice in README):
\begin{enumerate}
    \item \textbf{Micronaut}~--- lightweight, fast startup, minimal memory footprint.
    \item \textbf{Quarkus}~--- Kubernetes-native, optimized for containers.
    \item \textbf{Helidon}~--- Oracle's microservices library with reactive support.
    \item \textbf{Vert.x}~--- event-driven, non-blocking toolkit.
    \item \textbf{Plain Java}~--- no framework, manual dependency wiring.
          Acceptable if you demonstrate clean architecture.
\end{enumerate}


\section{Grading Criteria}

\begin{center}
\begin{tabular}{|l|c|l|}
\hline
\textbf{Problem} & \textbf{Points} & \textbf{Key Criteria} \\
\hline
1. Core Pipeline & 20 & Working sources, consumers, end-to-end demo \\
\hline
2. Processors \& Composition & 25 & 4+ strategies with proper PCM, chain, builder \\
\hline
3. Testing & 25 & Unit + integration tests, meaningful coverage \\
\hline
4. UI \& Visualization & 30 & Configuration UI + real-time waveform/spectrum \\
\hline
\textbf{Total} & \textbf{100} & \\
\hline
\end{tabular}
\end{center}

\textbf{Deductions may apply for:}
\begin{itemize}
    \item Treating individual bytes as audio samples (ignoring 16-bit PCM format)
    \item Code that compiles but produces noise/silence instead of correct audio
    \item Poor code organization, missing documentation, or copy-pasted code without understanding
    \item Tests that don't actually verify audio correctness (e.g., only checking array length)
\end{itemize}

\textbf{Bonus points (up to +15) for:}
\begin{itemize}
    \item Exceptionally clean architecture or creative design
    \item Implementing a genuinely interesting DSP algorithm (reverb, pitch shift, etc.)
    \item Visual pipeline editor or other innovative UI
    \item Particularly thorough or creative testing
\end{itemize}


\section{Blueprint Structure}

The starter code provides the following (your task is to extend and complete it):

\begin{center}
\small
\begin{tabular}{|l|l|}
\hline
\textbf{File} & \textbf{Purpose} \\
\hline
\texttt{audiostream/AudioStream.java} & Core I/O interface \\
\texttt{channel/Channel.java} & Thread-safe data buffer with subchannels \\
\texttt{channel/ObservableChannel.java} & Observer-pattern channel \\
\texttt{processing/AudioProcessingStrategy.java} & Strategy interface \\
\texttt{processing/VolumeControlStrategy.java} & Reference: proper PCM processing \\
\texttt{processing/AudioProcessingContext.java} & Strategy context \\
\texttt{processing/ProcessorChain.java} & \textit{Skeleton}: composite processor \\
\texttt{pipeline/Pipeline.java} & Pipeline interface \\
\texttt{pipeline/AudioPipeline.java} & \textit{Skeleton}: builder-based pipeline \\
\texttt{pin/DataPin.java} & Observer interface \\
\texttt{pin/AudioProcessorPin.java} & Concrete observer \\
\texttt{source/WAVFileReader.java} & Reference source \\
\texttt{source/SineWaveGenerator.java} & Test tone generator \\
\texttt{consumer/FileWriter.java} & Reference consumer \\
\texttt{converter/Converter.java} & Generic converter interface \\
\texttt{converter/SpeechToTextConverter.java} & Stub converter \\
\texttt{config/AudioSystemConfig.java} & Spring configuration \\
\texttt{config/ConfigManagerUI.java} & JavaFX UI skeleton \\
\texttt{util/SystemLogger.java} & Logging utility \\
\texttt{util/WAVUtils.java} & WAV header read/write utilities \\
\hline
\texttt{test/.../ChannelTest.java} & Sample: channel unit test \\
\texttt{test/.../VolumeControlStrategyTest.java} & Sample: processor unit test \\
\hline
\end{tabular}
\end{center}


\section{Tips and Resources}

\begin{itemize}
    \item \textbf{Start with SineWaveGenerator}: test your processors on generated tones
          before attempting file I/O or microphone capture. You can verify correctness
          mathematically (e.g., doubling volume should double sample values).

    \item \textbf{Java Sound API}: \texttt{javax.sound.sampled} provides
          \texttt{AudioInputStream}, \texttt{AudioSystem}, \texttt{SourceDataLine} (playback),
          and \texttt{TargetDataLine} (recording).

    \item \textbf{WAV file format}: A WAV file = 44-byte RIFF header + raw PCM data.
          Use the provided \texttt{WAVUtils} for header manipulation.

    \item \textbf{Threading}: Audio sources and sinks typically run in their own threads.
          Use \texttt{BlockingQueue} (already in Channel) for synchronization.
          Use \texttt{ExecutorService} for managed thread pools.

    \item \textbf{JavaFX Canvas for visualization}: Draw waveforms by mapping sample values
          to pixel coordinates. Use \texttt{AnimationTimer} or \texttt{Timeline}
          for smooth updates.

    \item \textbf{Echo/Delay algorithm hint}: maintain a circular buffer of past samples.
          Output $= $ current sample $+$ gain $\times$ sample from $N$ positions ago.

    \item \textbf{Useful test pattern}: generate a known sine wave, process it,
          verify mathematical properties of the output (amplitude, zero-crossings, etc.).
\end{itemize}

\end{document}
