\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{enumitem}

\usepackage[margin=0.7in]{geometry}

\usepackage{tikz}
\usetikzlibrary{matrix,arrows,decorations.pathmorphing,shapes.geometric,calc,snakes,backgrounds,arrows.meta}
\usepackage{xcolor}

\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}

\begin{document}
\pagestyle{plain}

\section*{Problem Sheet --- IMC Training}

\begin{center}
May 13, 2026
\end{center}

\textbf{Problem 1.} (IMC 2022, Day 1, Problem 2)
Let \( n \) be a positive integer. Find all \( n \times n \) real matrices \( A \) with only real eigenvalues
satisfying
\[
A + A^k = A^T
\]
for some integer \( k \geq n \).
\\

\textbf{Problem 2.} (IMC 2021, Day 1, Problem 2)
Let \( n \) and \( k \) be fixed positive integers, and let \( a \) be an arbitrary non-negative integer.
Choose a random \( k \)-element subset \( X \) of \( \{1, 2, \ldots, k + a\} \) uniformly and, independently of \( X \),
choose a random \( n \)-element subset \( Y \) of \( \{1, \ldots, k + n + a\} \) uniformly.
Prove that the probability
\[
\mathbb{P}\bigl(\min(Y) > \max(X)\bigr)
\]
does not depend on \( a \).
\\

\textbf{Problem 3.} (IMC 2020, Day 2, Problem 5)
Find all twice continuously differentiable functions \( f : \R \to (0, +\infty) \) satisfying
\[
f''(x)\, f(x) \geq 2\bigl(f'(x)\bigr)^2
\]
for all \( x \in \R \).
\\

\textbf{Problem 4.} (IMC 2022, Day 1, Problem 3)
Let \( p \) be a prime number. A flea is staying at point \( 0 \) of the real line. At each minute,
the flea has three possibilities: to stay at its position, or to move by \( 1 \) to the left or to the right.
After \( p - 1 \) minutes, it wants to be at \( 0 \) again. Denote by \( f(p) \) the number of its strategies to do this.
Find \( f(p) \) modulo \( p \).
\\

\textbf{Problem 5.} (IMC 2020, Day 2, Problem 7)
Let \( G \) be a group and \( n \geq 2 \) be an integer. Let \( H_1 \) and \( H_2 \) be two subgroups of \( G \) that satisfy
\[
[G : H_1] = [G : H_2] = n \quad \text{and} \quad [G : (H_1 \cap H_2)] = n(n - 1).
\]
Prove that \( H_1 \) and \( H_2 \) are conjugate in \( G \).
\\

\textbf{Problem 6.} (IMC 2021, Day 2, Problem 8)
Let \( n \) be a positive integer. At most how many distinct unit vectors can be selected in \( \R^n \)
such that from any three of them, at least two are orthogonal?
\\

\textbf{Problem 7.} (IMC 2022, Day 2, Problem 7)
Let \( A_1, A_2, \ldots, A_k \) be \( n \times n \) idempotent complex matrices such that
\[
A_i A_j = -A_j A_i \quad \text{for all } i \neq j.
\]
Prove that at least one of the given matrices has rank \( \leq \dfrac{n}{k} \).
(A matrix \( A \) is called idempotent if \( A^2 = A \).)
\\

\textbf{Problem 8.} (IMC 2020, Day 2, Problem 8)
Compute
\[
\lim_{n \to \infty} \frac{1}{\log \log n} \sum_{k=1}^{n} (-1)^k \binom{n}{k} \log k.
\]
(Here \( \log \) denotes the natural logarithm.)
\\

\textbf{Problem 9.} (IMC 2021, Day 2, Problem 7)
Let \( D \subseteq \C \) be an open set containing the closed unit disk \( \{z : |z| \leq 1\} \).
Let \( f : D \to \C \) be a holomorphic function, and let \( p(z) \) be a monic polynomial. Prove that
\[
|f(0)| \leq \max_{|z| = 1} |f(z)\, p(z)|.
\]
\\

\textbf{Problem 10.} (IMC 2020, Day 1, Problem 3)
Let \( d \geq 2 \) be an integer. Prove that there exists a constant \( C(d) \) such that the following holds:
for any convex polytope \( K \subset \R^d \), which is symmetric about the origin, and any \( \varepsilon \in (0, 1) \),
there exists a convex polytope \( L \subset \R^d \) with at most \( C(d)\, \varepsilon^{1 - d} \) vertices such that
\[
(1 - \varepsilon) K \subseteq L \subseteq K.
\]

\end{document}
