\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{enumitem}

\usepackage[margin=0.7in]{geometry} % Adjust the margins of document here.

\usepackage{tikz}                                          % Для простых рисунков в документе
\usetikzlibrary{matrix,arrows,decorations.pathmorphing,shapes.geometric,calc,snakes,backgrounds,arrows.meta}
\usepackage{xcolor}

\begin{document}
\pagestyle{plain}

\section*{Math Analysis Olympiad Problems}

\begin{center}
February 2025
\end{center}

\textbf{Problem 1. Continuity and Differentiability at a Point.}
Consider the function
\[
f(x) = \begin{cases}
x^2 \sin\left(\frac{1}{x}\right), & x\neq 0, \\
0, & x=0.
\end{cases}
\]
\begin{enumerate}
    \item Prove that \(f\) is continuous at \(x=0\).
    \item Decide whether \(f\) is differentiable at \(x=0\) and, if so, compute \(f'(0)\).
\end{enumerate}
\\

\textbf{Problem 2. Lipschitz Continuity via Bounded Derivative.}
Let \(f:[a,b]\to \mathbb{R}\) be a differentiable function with a bounded derivative; that is, there exists \(M>0\) such that
\[
    |f'(x)| \le M \quad \text{for all } x \in (a,b).
\]
Prove that \(f\) is Lipschitz continuous on \([a,b]\); i.e., show that for all \(x,y\in [a,b]\),
\[
    |f(x)-f(y)| \le M |x-y|.
\]
\\

\textbf{Problem 3. A Telescoping Series with Alternating Terms.}
Study the convergence of the series
    \[
    \sum_{n=1}^\infty \left( \frac{(-1)^n}{\sqrt{n+1}} - \frac{(-1)^n}{\sqrt{n}} \right)
    \]
Determine whether the series converges absolutely, conditionally or diverges.
Provide a complete justification.
\\

\textbf{Problem 4.}
Let $f \in C^1(a,b)$. Suppose
\[
\lim_{x \to a^+} f(x) = +\infty,
\quad
\lim_{x \to b^-} f(x) = -\infty,
\]
and
\[
  f'(x) + f^2(x) \ge -1
\quad
\text{for all } x \in (a,b).
\]
Prove that $b-a > \pi$ and give an example where $b-a = \pi$.
\\

\textbf{Problem 5.}
Let \( f \in C^1[a,b] \), \( f(a) = 0 \) and suppose that \( \lambda \in \mathbb{R} \), \( \lambda > 0 \), is such that
\[
|f'(x)| \leq \lambda |f(x)|
\]
for all \( x \in [a,b] \). Is it true that \( f(x) = 0 \) for all \( x \in [a,b] \)?
\\

\textbf{Problem 6.}
Find \[
\lim_{N \to \infty} \frac{\ln^2 N}{N} \sum_{k=2}^{N-2} \frac{1}{\ln k \cdot \ln (N-k)}.
\]
Note that \( \ln \) denotes the natural logarithm.
\\

\textbf{Problem 7.}
Let \( F : (1, \infty) \to \mathbb{R} \) be the function defined by
\[
    F(x) := \int_x^{x^2} \frac{dt}{\ln t}
\]
Show that \( F \) is one-to-one (i.e., injective) and find the range (i.e., set of values) of \( F \).
\\

\textbf{Problem 8.}
Let \( \{b_n\}_{n=0}^{\infty} \) be a sequence of positive real numbers such that \( b_0 = 1 \),
\[
b_n = 2 + \sqrt{b_{n-1}} - 2\sqrt{1+\sqrt{b_{n-1}}}.
\]
Calculate
\[
\sum_{n=1}^{\infty} b_n 2^n.
\]
\\

\textbf{Problem 9.}
Evaluate the definite integral
\[
\int_{-\pi}^{\pi} \frac{\sin nx}{(1 + 2^x) \sin x} \,dx,
\]
where \( n \) is a natural number.
\\

\textbf{Problem 10.}
\begin{itemize}
    \item[(i)] Prove that
    \[
    \lim_{x \to +\infty} \sum_{n=1}^{\infty} \frac{nx}{(n^2 + x)^2} = \frac{1}{2}.
    \]
    \item[(ii)] Prove that there is a positive constant \( c \) such that for every \( x \in [1, \infty) \) we have
    \[
    \left| \sum_{n=1}^{\infty} \frac{nx}{(n^2 + x)^2} - \frac{1}{2} \right| \leq \frac{c}{x}.
    \]
\end{itemize}

\end{document}
