\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{enumitem}

\usepackage[margin=0.7in]{geometry} % Adjust the margins of document here.

\usepackage{tikz}                                          % Для простых рисунков в документе
\usetikzlibrary{matrix,arrows,decorations.pathmorphing,shapes.geometric,calc,snakes,backgrounds,arrows.meta}
\usepackage{xcolor}

\begin{document}
\pagestyle{plain}

\section*{Linear Algebra Olympiad Problems}

\begin{center}
February 2025
\end{center}

\textbf{Problem 1.}
Given the matrix
\[
A_n = \begin{pmatrix}
1 & \frac{2}{n} & \frac{6}{n} \\
\frac{3}{n} & 1 & 0 \\
-\frac{1}{n} & 0 & 1
\end{pmatrix}
\]
Calculate \( \lim\limits_{n \to \infty} A_n^n \).
\\

\textbf{Problem 2.}
Let \( A \) and \( B \) be nonzero matrices of size \( n \times n \), where \( n \geq 2 \).
It is known that \( ABA = A \). Does it follow that \( BAB = B \)?
\\

\textbf{Problem 3.}
Suppose that for matrices \( A \) and \( B \), the equality
\[
AB = \alpha A + \beta B
\]
holds, where \( \alpha \) and \( \beta \) are some nonzero numbers. Prove that \( BA = AB \).
\\

\textbf{Problem 4.}
Let \( A, B, C \) be square matrices of the same size, where \( A \) is non-singular. Prove that if
\[
(A - B)CA = B,
\]
then
\[
AC(A - B) = B.
\]
\\

\textbf{Problem 5.}
Let \( A \) and \( B \) be distinct real square matrices. If
\[
A^3 = B^3 \quad \text{and} \quad A^2 B = B^2 A,
\]
can the matrix \( A^2 + B^2 \) be invertible?
\\

\textbf{Problem 6.}
All elements of the third-order matrix are squares of odd numbers.
Prove that its determinant is divisible by 64.
\\

\textbf{Problem 7.}
Let \( A \) and \( B \) be square matrices such as that
\[
A^2 = A, \quad B^2 = B, \quad AB = BA.
\]
What values can the determinant of the matrix \( A - B \) take?
\\

\textbf{Problem 8.}
The matrices \( A \) and \( B \) do not commute, i.e. \( AB \neq BA \). Can it happen that the matrices \( A^2 \) and \( B^2 \) commute?
\\

\textbf{Problem 9.}
Compute the determinant of the matrix \( A = (a_{i,j}) \) of size \( n \times n \) with the general term \( a_{i,j} = \max(i, j) \).
\\

\textbf{Problem 10.}
Compute the determinant:
\[
\begin{vmatrix}
0 & 1 & 1 & 1 & \dots & 1 \\
1 & 1 & 0 & 0 & \dots & 0 \\
1 & 0 & \frac{1}{2} & 0 & \dots & 0 \\
1 & 0 & 0 & \frac{1}{3} & \dots & 0 \\
\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
1 & 0 & 0 & 0 & \dots & \frac{1}{n}
\end{vmatrix}
\]
\end{document}
