\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{enumitem}

\usepackage[margin=0.7in]{geometry}

\usepackage{tikz}
\usetikzlibrary{matrix,arrows,decorations.pathmorphing,shapes.geometric,calc,snakes,backgrounds,arrows.meta}
\usepackage{xcolor}

\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\F}{\mathbb{F}}

\begin{document}
\pagestyle{plain}

\section*{Mock Olympiad (IMC), Round 1}

\begin{center}
June 28, 2026 \\
Time allowed: 5 hours. Each problem is worth 10 points.
\end{center}

\textbf{Problem 1.} % (IMC 2013, Day 2, Problem 1)
Let \( z \) be a complex number with \( |z + 1| > 2 \). Prove that \( |z^3 + 1| > 1 \).
\\

\textbf{Problem 2.} % (IMC 2012, Day 1, Problem 2)
Let \( n \) be a fixed positive integer. Determine the smallest possible rank of an \( n \times n \) matrix that has zeros along the main diagonal and strictly positive real numbers off the main diagonal.
\\

\textbf{Problem 3.} % (IMC 2013, Day 1, Problem 3)
There are \( 2n \) students in a school (\( n \in \N \), \( n \geq 2 \)). Each week \( n \) students go on a trip. After several trips the following condition was fulfilled: every two students were together on at least one trip. What is the minimum number of trips needed for this to happen?
\\

\textbf{Problem 4.} % (IMC 2012, Day 1, Problem 4)
Let \( f : \R \to \R \) be a continuously differentiable function that satisfies \( f'(t) > f(f(t)) \) for all \( t \in \R \). Prove that \( f(f(f(t))) \leq 0 \) for all \( t \geq 0 \).
\\

\textbf{Problem 5.} % (IMC 2012, Day 1, Problem 5)
Let \( a \) be a rational number and let \( n \) be a positive integer. Prove that the polynomial \( X^{2^n}(X + a)^{2^n} + 1 \) is irreducible in the ring \( \Q[X] \) of polynomials with rational coefficients.

\end{document}
