\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{enumitem}

\usepackage[margin=0.7in]{geometry} % Adjust the margins of document here.

\usepackage{tikz}                                          % Для простых рисунков в документе
\usetikzlibrary{matrix,arrows,decorations.pathmorphing,shapes.geometric,calc,snakes,backgrounds,arrows.meta}
\usepackage{xcolor}

\begin{document}
\pagestyle{plain}

\section*{Selected Beautiful Problems: IMC 2001--2006}

\begin{center}
April 22, 2026
\end{center}

\textbf{Problem 1.} (IMC 2001, Day 2, Problem 3)
Find the maximum number of points on a sphere of radius \( 1 \) in \( \mathbb{R}^n \) such that the distance between any two of these points is strictly greater than \( \sqrt{2} \).
\\

\textbf{Problem 2.} (IMC 2005, Day 2, Problem 2)
Let \( f : \mathbb{R} \to \mathbb{R} \) be a function such that \( (f(x))^n \) is a polynomial (in \( x \)) for every integer \( n \geq 2 \). Does it follow that \( f \) itself is a polynomial?
\\

\textbf{Problem 3.} (IMC 2003, Day 1, Problem 4)
Determine the set of all pairs \( (a, b) \) of positive integers for which the set of positive integers can be decomposed into two sets \( A \) and \( B \) such that
\[
a \cdot A = b \cdot B.
\]
(Here \( a \cdot A = \{ a \cdot x : x \in A \} \).)
\\

\textbf{Problem 4.} (IMC 2003, Day 1, Problem 6)
Let \( f(z) = a_n z^n + a_{n-1} z^{n-1} + \cdots + a_1 z + a_0 \) be a polynomial with real coefficients. Prove that if all roots of \( f \) lie in the left half-plane \( \{ z \in \mathbb{C} : \operatorname{Re} z < 0 \} \), then
\[
a_k a_{k+3} < a_{k+1} a_{k+2}
\]
for every \( k = 0, 1, \ldots, n-3 \).
\\

\textbf{Problem 5.} (IMC 2004, Day 2, Problem 6)
For \( n \geq 0 \) define matrices \( A_n \) and \( B_n \) by \( A_0 = B_0 = (1) \) and for \( n > 0 \),
\[
A_n = \begin{pmatrix} A_{n-1} & A_{n-1} \\ A_{n-1} & B_{n-1} \end{pmatrix}, \qquad
B_n = \begin{pmatrix} A_{n-1} & A_{n-1} \\ A_{n-1} & 0 \end{pmatrix}.
\]
Let \( S(M) \) denote the sum of all entries of a matrix \( M \). Prove that
\[
S(A_n^{\,k-1}) = S(A_k^{\,n-1}) \qquad \text{for every } n, k \geq 1.
\]
\\

\textbf{Problem 6.} (IMC 2005, Day 1, Problem 4)
Find all polynomials \( P(x) = a_n x^n + a_{n-1} x^{n-1} + \cdots + a_1 x + a_0 \) (with \( a_n \neq 0 \)) satisfying the following two conditions:
\begin{enumerate}
    \item the coefficient sequence \( (a_0, a_1, \ldots, a_n) \) is a permutation of \( (0, 1, \ldots, n) \);
    \item all roots of \( P(x) \) are rational.
\end{enumerate}
\\

\textbf{Problem 7.} (IMC 2005, Day 2, Problem 1)
Let \( f(x) = x^2 + bx + c \) with \( b, c \in \mathbb{R} \), and let
\[
M = \{ x \in \mathbb{R} : |f(x)| < 1 \}.
\]
Clearly \( M \) is either empty or a union of disjoint open intervals; denote the sum of their lengths by \( |M| \). Prove that \( |M| \leq 2\sqrt{2} \).
\\

\textbf{Problem 8.} (IMC 2006, Day 1, Problem 1)
Let \( f : \mathbb{R} \to \mathbb{R} \) be a real function. Prove or disprove each of the following statements:
\begin{enumerate}
    \item[(a)] If \( f \) is continuous and \( \operatorname{range}(f) = \mathbb{R} \), then \( f \) is monotonic.
    \item[(b)] If \( f \) is monotonic and \( \operatorname{range}(f) = \mathbb{R} \), then \( f \) is continuous.
    \item[(c)] If \( f \) is monotonic and continuous, then \( \operatorname{range}(f) = \mathbb{R} \).
\end{enumerate}
\\

\textbf{Problem 9.} (IMC 2006, Day 1, Problem 5)
Let \( a, b, c, d, e > 0 \) be real numbers such that
\[
a^2 + b^2 + c^2 = d^2 + e^2 \qquad \text{and} \qquad a^4 + b^4 + c^4 = d^4 + e^4.
\]
Compare \( a^3 + b^3 + c^3 \) with \( d^3 + e^3 \).
\\

\textbf{Problem 10.} (IMC 2006, Day 2, Problem 4)
Let \( v_0 \) be the zero vector in \( \mathbb{R}^n \) and let \( v_1, v_2, \ldots, v_{n+1} \in \mathbb{R}^n \) be such that the Euclidean norm \( |v_i - v_j| \) is rational for every \( 0 \leq i, j \leq n+1 \). Prove that \( v_1, v_2, \ldots, v_{n+1} \) are linearly dependent over the rationals.

\end{document}
